### 2013-09-10 thesis/src/chapters/chapter-2.tex
Added amdahl chart, new chapter

<mapping layer => actions>

With all that said, there is no silver bullet - not matter what underlying mechanism platform provider decides to use, the application developer is still responsible for creating an application with scaling in-mind. This statement has been already proven in 1967 by Amdahl law, which in short states that sequential component of parallel algorithms impacts efficiency for a sufficiently large number processors \cite{Am67}. In other words, adding supplementary resources to a poorly written application (i.e. having a lot of sequential or synchronized components) can be beneficial only to a certain degree.

@@

Among the mod\_proxy\_balancer features we may distinguish:
\begin{itemize}
 \item support for different load-balancing algorithms:
    \begin{itemize}
      \item Request Counting Algorithm - load is distributed the requests among the various workers, ensuring that each gets their configured share of the number of requests
      \item Weighted Traffic Counting Algorithm - variation of above-mentioned algorithm with a difference that it is focused on bytes rather than number of request
      \item Pending Request Counting Algorithm - scheduler keeps track of how many requests each worker is assigned at present. A new request is automatically assigned to the worker with the lowest number of active requests
    \end{itemize}

>>>>

With all that said, there is no silver bullet - not matter what underlying mechanism platform provider decides to use, the application developer is still responsible for creating an application with scaling in-mind. This statement has been already proven in 1967 by Amdahl law, which in short states that sequential component of parallel algorithms impacts efficiency for a sufficiently large number processors \cite{Am67} as shown in \ref{ch2:amdahl-lawl}. In other words, adding supplementary resources to a poorly written application (i.e. having a lot of sequential or synchronized components) can be beneficial only to a certain degree.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-2/amdahl-law}
  \end{center}
  \caption{Amdahl's law}
  \label{ch2:amdahl-law}
\end{figure}

@@

Among the mod\_proxy\_balancer features we may distinguish:
\begin{itemize}
 \item support for different load-balancing algorithms:
    \begin{itemize}
      \item \textit{request counting algorithm} - load is distributed the requests among the various workers, ensuring that each gets their configured share of the number of requests
      \item \textit{weighted traffic counting algorithm} - variation of above-mentioned algorithm with a difference that it is focused on bytes rather than number of request
      \item \textit{pending request counting algorithm} - scheduler keeps track of how many requests each worker is assigned at present. A new request is automatically assigned to the worker with the lowest number of active requests
    \end{itemize}
